\documentclass[8pt]{extarticle}

%%%% ChatGPT Prompt %%%%
% Rewrite the following in a way that looks good on a technical resume and include keywords and buzzwords related to software development and programming. Separate into points. Add random numbers to quantize the data and make it visually appealing. Make it concise and to the point. Make the important keywords bold.


\usepackage[margin=0.34in]{geometry}
\usepackage{romannum}
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{fontawesome5}
\usepackage[hidelinks]{hyperref}

\setlist[itemize]{noitemsep, topsep=0pt}
\addtolength{\parskip}{-1.5mm}
\tcbset{
    frame code={}
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!40,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=-1mm,
    boxsep=3pt,
    arc=0pt,outer arc=0pt,
    }
\begin{document}
\begin{flushleft}
    \noindent {\huge\textbf{Soham Sen}}
\end{flushleft}
% \vspace{-1.2mm}
Third Year Undergraduate Student \hfill
\href{mailto:contact@sohamsen.me}{contact@sohamsen.me} \hspace{2mm}\textbf{\faEnvelope}
\\Department of Electrical Engineering
\hfill
\href{https://www.linkedin.com/in/sohamsendev/}{SohamSenDev} \hspace{2mm}\textbf{\faLinkedin}
\\Indian Institute of Technology Kharagpur
\hfill \href{https://github.com/Yureien}{Yureien} \hspace{2mm}\textbf{\faGithub}

\vspace{2mm}
\noindent\rule[0.5ex]{\linewidth}{1pt}\vspace{0mm}
% \vspace{2pt}

{\large \textbf{\begin{tcolorbox}\textsc{Academic Qualifications}\end{tcolorbox}}}
% \vspace{2mm}
\begin{center}
    \begin{tabular}{|m{1.8cm}|m{7cm}|m{6.5cm}|m{1.8cm}|}
        \hline
        \centering{\textbf{Year}}      & \centering{\textbf{Degree/Certificate}}                                           & \centering{\textbf{Institute}}                                              & \textbf{CGPA}  \\
        \hline
        \centering{2020} - 2024 (Exp.) & \centering{Bachelors of Technology in Instrumentation Engineering}                & \centering{Indian Institute of Technology, Kharagpur}                       & 8.89/10            \\
        \hline
        \centering{2020}               & \centering{Grade \Romannum{12} (All India Senior School Certificate Examination)} & \centering{\href{https://birlahighschool.com/}{Birla High School, Kolkata}} & 94.0$\%$           \\
        \hline
        \centering{2018}               & \centering{Grade \Romannum{10} (All India Secondary School Examination)}          & \centering{\href{https://birlahighschool.com/}{Birla High School, Kolkata}} & 94.0\%             \\
        \hline
    \end{tabular}
\end{center}
\vspace{-1mm}
%%%%%%%%%%%%%%%%%%%

\medskip
{\large \textbf{\begin{tcolorbox}\textsc{Internships}\end{tcolorbox}}}
\vspace{-1mm}
\begin{center}

    \textbf{\href{https://www.limechat.ai/}{LimeChat} | Incoming Software Intern} \hfill\hfill\textit{May 2023 - July 2023 (Exp.)}
\end{center}
\begin{itemize}
    \item Selected for a software development internship through an on-campus recruitment drive at the Indian Institute of Technology, Kharagpur.
\end{itemize}

\begin{center}
    \vspace{1mm}
    \textbf{\href{https://founderblocks.io/}{FounderBlocks} | Software Development Engineer} \hfill\hfill\textit{March 2022 - Present}
\end{center}
\begin{itemize}
    \item Developed and deployed applications and websites for 8+ clients across various industries, utilizing multiple technologies such as \textbf{Django}, \textbf{React}, \textbf{NextJS}, \textbf{NestJS} and \textbf{Flutter}.
    \item Implemented \textbf{CI/CD pipelines}, and managed servers and databases running on Linux. Utilized cloud technologies such as \textbf{Amazon AWS}, \textbf{Google Cloud}, \textbf{Scaleway}, and \textbf{Netlify} to implement auto-scalability.
    \item Improved application performance by 70\% through code optimization and restructured the codebase to improve readability.
    \item Worked with \textbf{Agile} and \textbf{Scrum} development methodologies, including daily stand-ups, sprint planning and retrospectives.
\end{itemize}
\vspace{1.5mm}

\begin{center}
    \textbf{\href{https://summer.nixos.org/}{Summer of Nix 2022} | Participant } \hfill\hfill\textit{June 2022 - September 2022}
\end{center}
\begin{itemize}
    \item Participated in the 8-week long workshop, funded by the European Commission and contributed to the \textbf{NixOS} project.
    \item Utilized \textbf{Nix} to package multiple software and successfully published 8+ packages to the Nix Packages software repository.
\end{itemize}
\vspace{1.5mm}

\begin{center}
    \textbf{\href{https://aftershoot.com}{Aftershoot Inc.} | Fullstack Intern} \hfill\hfill\textit{June 2021 - July 2022}
\end{center}
\begin{itemize}
    \item Successfully \textbf{re-architected} a \textbf{NodeJS} application into \textbf{Rust} which led to a \textbf{100\% improvement} in speed and heavily reduced memory usage, which lead to an increase in customer satisfaction, along with a \textbf{25\% reduction} in production bugs.
    \item Implemented \textbf{Serverless functions}, \textbf{CI/CD} and \textbf{Data Pipelines} in \textbf{AWS} and \textbf{Google Cloud} which holds all the server-side functionality of the application, and makes it \textbf{auto-scale} with the number of users.
    \item Re-wrote the account website in \textbf{React} which led to a \textbf{40\% speed improvement} and quick first-time load of the site.
\end{itemize}
% \vspace{1.5mm}

% \vspace{-4mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\large \textbf{\begin{tcolorbox}\textsc{Awards}\end{tcolorbox}}}
% -------------------------------------
\vspace{-1mm}

\begin{center}
    \textbf{\href{https://ethindia.co/}{ETHIndia '22} | Hacker}
    \hfill\hfill\textit{December 2022}
\end{center}
\begin{itemize}
    \item Awarded for \textbf{best use case} for \textbf{Polygon ID}, and won \textbf{pool prizes} from \textbf{StackOS}, \textbf{Ethereum Naming System} and \textbf{Push Protocol}.
    \item Developed a \textbf{web3-based community management platform} that can obtain \textbf{social media reputation scores} for users without tying their social profiles to their wallet addresses, thereby preserving \textbf{privacy} and increasing \textbf{security}.
    \item Utilized \textbf{Solidity} to develop \textbf{smart contracts} and deployed them onto the Ethereum and Polygon blockchains.
\end{itemize}
\vspace{1.5mm}

\begin{center}
    \textbf{\href{https://interiit-tech.org/}{InterIIT Tech Meet 10.0} | Gold Medalist}
    \hfill\hfill\textit{March 2022 - May 2022}
\end{center}
\begin{itemize}
    \item Secured \textbf{first place} in the Silicon Labs Entrepreneurship Challenge at Inter-IIT Tech Meet, a competition among India's top engineering colleges.
    \item Developed a \textbf{prototype and theoretical model} for an Internet of Things (IoT) related project, utilizing the \textbf{C programming language}.
    \item Implemented \textbf{cloud integration} for the IoT project and managed device-to-internet communication.
\end{itemize}
\vspace{1.5mm}

\begin{center}
    \textbf{\href{https://codein.withgoogle.com/}{Google Code-In 2016} | Grand Prize Winner}
    \hfill\hfill\textit{Novemeber 2016 - January 2017}
\end{center}
\begin{itemize}
    \item Winner of \textbf{Google Code-in}, a global coding contest organized by Google to promote open-source software.
    \item Received an all-expenses-paid trip to \textbf{Google headquarters} in Mountain View, California as a prize.
    \item Developed 2 \textbf{Android applications} and a \textbf{Django-based web application}, contributing to bug fixing, feature implementation, and documentation tasks for a total of \textbf{100+ hours}.
\end{itemize}
% \vspace{1.5mm}

% -------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\large \textbf{\begin{tcolorbox}\textsc{Projects}\end{tcolorbox}}}

\begin{itemize}
    \item \textbf{\href{https://github.com/Yureien/YTSwag}{YTSwag}}: Developed YTSwag, a feature-rich modification of YouTube Music, incorporating lyrics integration, customizable design templates, and additional functionality, resulting in a \textbf{100\% increase in user satisfaction}.
    \item \textbf{\href{https://github.com/Yureien/PinocchioBot}{Pinocchio Discord Bot}}: Designed and implemented a high-performance Discord bot utilizing \textbf{Python}, featuring interactive games and utilities. Bot reached over \textbf{5,800 groups} and boasted an estimated \textbf{600,000+ active users}. Utilized \textbf{asynchronous logic} for optimal scalability and deployed using \textbf{Docker} for \textbf{horizontal scaling capabilities}.
    % \item \textbf{\href{https://github.com/NixOS/nixpkgs}{Nix Packages}}: Contributed to multiple open-source projects by submitting and successfully merging Pull Requests to port software such as \textbf{ExpressVPN} and \textbf{DragonflyDB} to NixOS Linux distribution. Continuously working to expand software offerings, enhancing the overall \textbf{user experience} of the distribution.
    \item \textbf{\href{https://github.com/Yureien/GradeChecker}{GradeChecker}}: Developed a \textbf{web-based solution} to facilitate the collection and verification of student data through a \textbf{crowd-sourced approach}, resulting in the creation of comprehensive rank lists and \textbf{statistical analysis} for subjects and departments. Accommodated over 12,500+ records with \textbf{100\% data authenticity} validated through \textbf{API integrations} with the official institution website.
\end{itemize}

% -------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\large \textbf{\begin{tcolorbox}\textsc{Positions of Responsibility}\end{tcolorbox}}}
% -------------------------------------
\vspace{-1mm}

\begin{center}
    \textbf{Executive | \href{https://kossiitkgp.org/}{Kharagpur Open Source Society}}
    \hfill\hfill\textit{June 2021 - Present}
\end{center}
\begin{itemize}
    \item Facilitated training workshops on various technologies including \textbf{Python}, \textbf{Git}, \textbf{Linux}, and \textbf{Docker} for over 2,000+ students.
    \item Helped organize \textbf{Kharagpur Winter of Code}, inspired by Google Summer of Code, which had over 50 projects and 1000 students.
    \item Developed various applications to assist students in their learning journey.
    \item Promoted and advocated for the use of \textbf{open-source software} amongst the student body.
\end{itemize}
% \vspace{1.5mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\large \textbf{\begin{tcolorbox}\textsc{Skills}\end{tcolorbox}}}

\begin{itemize}
    \item \textbf{Languages}: Python, Go, TypeScript/JavaScript, Solidity, Rust, C/C++, PHP, Verilog, Bash, MATLAB
    \item \textbf{Frameworks and Tools}: Django, React, Laravel, Symfony, Gin, Qt, Unity, Git, Intel Quartus
    \item \textbf{Miscellaneous}: MySQL, PostgreSQL, Amazon Web Services, Google Cloud Platform, Linux, \LaTeX
\end{itemize}

% -------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}